---
title: "homework chapter2"
author: "王柳盈"
date: "2017年2月27日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Read the manual of package "Performance Analytics"

```{r}
#install.packages("PerformanceAnalytics")
library("PerformanceAnalytics")
help(package="PerformanceAnalytics")
library("quantmod")
getSymbols("^GSPC",src="yahoo",from="1990-1-1",to=Sys.Date())
getSymbols("BABA",src="yahoo",from="2015-1-1",to=Sys.Date())
```

2. Draw the following graphic using "chart.Correlation"

chart.Correlation(R, histogram = TRUE, method = c("pearson", "kendall",
  "spearman"), ...)

```{r}
#?chart.Correlation
head(GSPC)
chart.Correlation(GSPC[,4:5])
```

3. Draw the following graphic using "chart.TimeSeries"

chart.TimeSeries(R, auto.grid = TRUE, xaxis = TRUE, yaxis = TRUE,
  yaxis.right = FALSE, type = "l", lty = 1, lwd = 2, las = par("las"),
  main = NULL, ylab = NULL, xlab = "", date.format.in = "%Y-%m-%d",
  date.format = NULL, xlim = NULL, ylim = NULL,
  element.color = "darkgray", event.lines = NULL, event.labels = NULL,
  period.areas = NULL, event.color = "darkgray",
  period.color = "aliceblue", colorset = (1:12), pch = (1:12),
  legend.loc = NULL, ylog = FALSE, cex.axis = 0.8, cex.legend = 0.8,
  cex.lab = 1, cex.labels = 0.8, cex.main = 1, major.ticks = "auto",
  minor.ticks = TRUE, grid.color = "lightgray", grid.lty = "dotted",
  xaxis.labels = NULL, ...)
```{r}
#?chart.TimeSeries
head(BABA)
chart.TimeSeries(BABA[,6],grid.color="red")
#时间区间调整用参数xlim
```

