---
title: "lecture note 5"
author: "王柳盈"
date: "2017年4月18日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,eval=F)
```

##ANOVA
St=Se+Sa
St=sum of square total
Se=sum of square within group
Sa=sum of square between group
$S_T=\sum_i^r\sum_j^{n_i}(x_{ij}-\bar x)^2   \  \bar x=\frac{1}{n}\sum_i^r\sum_j^{n_i}x_{ij}$ 
$S_E=\sum_i^r\sum_j^{n_i}(x_{ij}-\bar x_i)^2   \  \bar x_i=\frac{1}{n_i}\sum_j^{n_i}x_{ij}$
$S_A=\sum_i^r\sum_j^{n_i}(\bar x_{i}-\bar x)^2=\sum_{i=1}^r n_i(\bar x_i-\bar x)^2$
$F=\frac{S_A/r-1}{S_E/n-r}  F_{r-1,n-r} $


```{r}
library("foreign")
sales<-read.dta("sales.dta")
class(sales$color)
sales$color<-factor(sales$color)
plot(sales$sales ~ sales$color,col="green")
aggregate(sales$sales,by=list(sales$color),FUN=mean)
fit <- aov(sales~color,data=sales)
summary(fit)
View(sales)
```

##Two-way factorial ANOVA
```{r}
attach(ToothGrowth)
table(supp, dose)
aggregate(len, by = list(supp, dose), FUN = mean)
aggregate(len, by = list(supp, dose), FUN = sd)
fit <- aov(len ~ supp * dose)#考虑交叉项
fit <- aov(len ~ supp + dose)#不考虑交叉项
summary(fit)
```

###an example

```{r}
x <- pretty(c(-3,3), 60)#breakpoint
```

##generate sample
Generating multivariate normal data

```{r}
set.seed(20)
x <- rnorm(100)
e <- rnorm(100,0,2)
y <- 0.5+2*x+e
summary(y)
qqnorm(y)
qqline(y,lty=2)
shapiro.test(y)
```

##example:buffon's needle

```{r}
install.packages("animation")
library(animation)
windows(7,7)
buffon.needle(namx=50,interval=0)

buffon <- function(n,l=0.8,d=1)
{
  k=0#count
  theta <- runif(n,0,pi)#angle
  x <- runif(n,0,d/2)#positions of central point
  for (i in 1:n)
  {
    if(x[i]<=1/2*sin(theta[i]))
      k <- k+1
  }
  (pi_simulate <- 2*l*n/(k*d))
}
buffon(1000000)
```

##central limit theorem

##monte carlo integration
